\documentclass[11pt]{article}

\usepackage[margin=0.55in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern} 
\usepackage{microtype}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{tikz}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.18\baselineskip}

% Page style (multi-page academic CV)
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[C]{\thepage}

% --- Styling ---
\definecolor{cvaccent}{HTML}{1F4E79}
\hypersetup{colorlinks=true, urlcolor=cvaccent, linkcolor=cvaccent}

\titleformat{\section}{\large\bfseries\color{cvaccent}}{}{0pt}{}[\vspace{-0.75em}\color{cvaccent}\rule{\linewidth}{0.6pt}\vspace{-0.2em}]
\titlespacing*{\section}{0pt}{0.35em}{-0.1em}

% --- Simple CV helpers ---
\newcommand{\name}[1]{\textbf{\LARGE #1}}
\newcommand{\contact}[1]{\small #1}
\newenvironment{cvitems}{%
  \setlength{\parskip}{0pt}%
\begin{itemize}[leftmargin=*, itemsep=0.1em, topsep=0em, partopsep=0em, parsep=0pt]}{
  \end{itemize}}
\newcommand{\cventry}[4]{%
  \noindent
  \begin{tabular*}{\textwidth}{@{}p{0.75\textwidth}@{\extracolsep{\fill}}r@{}}
    \textbf{#1} & \textit{#4} \\
    \textit{#2} & #3 \\
  \end{tabular*}
  \vspace{-0.4em}
}

\begin{document}

% ===== Header =====
\begin{tabularx}{\linewidth}{@{}X r@{}}
  \name{Yuxuan Zhang} & \contact{\href{https://yuxuanzhang271.github.io}{yuxuanzhang271.github.io}}\\
  \contact{(65) 8941--6785} & \contact{\href{https://github.com/yuxuanzhang271}{github.com/yuxuanzhang271}}\\
  \contact{\href{mailto:e1216649@u.nus.edu}{e1216649@u.nus.edu}} & \contact{\href{https://www.linkedin.com/in/yuxuanzhang271}{linkedin.com/in/yuxuanzhang271}}\\
\end{tabularx}

% ===== Skills =====
\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
  \textbf{Coding:} & Python, C/C++, Bash (Shell), SQL, MATLAB, R, Verilog, Java, C\#, JavaScript/TypeScript \\
  \textbf{Tools:} & Linux, Git, CMake, Docker, CUDA, ROS/ROS2, PyTorch, TensorFlow, OpenCV, PCL, Open3D, Isaac Gym/Sim, MuJoCo \\
  & Unity, LabVIEW, Altium Designer, AutoCAD, SolidWorks, Multisim, Keil $\mu$Vision, KiCad \\
  \textbf{Languages:} & Chinese (native), English (fluent) \\
\end{tabularx}

% ===== Education =====
\section{Education}
\cventry{Master in Artificial Intelligence Systems}{National University of Singapore}{Singapore}{Aug 2025 -- Present}
\begin{cvitems}
\item Relevant Coursework: Robotic Systems, Natural Language Processing, Pattern Recognition, Machine Reasoning
\end{cvitems}

\cventry{Graduate Diploma in System Analysis}{National University of Singapore}{Singapore}{Jul 2023 -- Jan 2025}
\begin{cvitems}
\item GPA: \textit{4.11/5.00}. Focus: Machine Learning Infrastructure and Scalable System Design.
\end{cvitems}

\cventry{Bachelor in Intelligent Test \& Control Engineering}{Harbin Institute of Technology}{China}{Sep 2020 -- Jun 2024}
\begin{cvitems}
\item GPA: \textit{4.02/5.00}. Thesis Focus: Precision Measurement, Embedded Systems, and Real-time Distributed Control.
\end{cvitems}

% ===== Publications =====
\section{Publications}
\begin{enumerate}[leftmargin=*, itemsep=0.25em, topsep=0.2em]
  \item Chongkai Gao, Zixuan Liu, Zhenghao Chi, Junshan Huang, Xin Fei, Yiwen Hou, \textbf{Yuxuan Zhang}, Yudi Lin, Zhirui Fang, Zeyu Jiang, Lin Shao. ``VLA-OS: Structuring and Dissecting Planning Representations and Paradigms in Vision-Language-Action Models.'' \textit{NeurIPS 2025} (accepted). \href{https://arxiv.org/abs/2506.17561}{arXiv:2506.17561}.
    \begin{cvitems}
    \item Developed \textbf{VLA-OS}, a modular framework to evaluate Action-Only, Integrated, and Hierarchical planning paradigms.
    \item Investigated \textbf{visually-grounded hierarchical planning}, demonstrating its superior zero-shot generalization and long-horizon performance across LIBERO, COLOSSEUM, and DexArt benchmarks.
    \end{cvitems}
\end{enumerate}

% ===== Preprints =====
\section{Preprints}
\begin{enumerate}[leftmargin=*, itemsep=0.25em, topsep=0.2em]
  \item \textbf{Yuxuan Zhang}. ``CCTA: Safety- and Capability-Constrained Tool Arbitration for Long-Horizon Embodied Decision Making.'' \textit{Preprint 2026}.
    \begin{cvitems}
    \item Proposed \textbf{CCTA}, a hierarchical framework for heterogeneous tool arbitration (VLA, RL, IK) under hard safety and morphology constraints.
    \item Formulated arbitration as a \textbf{constrained optimization problem}, integrating Control Barrier Functions (CBFs) for safety projection and ROS 2 LifecycleNodes for compute-aware scheduling.
    \end{cvitems}
  \item Chongkai Gao, Jieao Shi, Xuchuan Huang, Mu Zhaoyu, \textbf{Yuxuan Zhang}, et al. ``ManiLadder: Benchmarking Manipulation Intelligence Frontier via a Categorized and Multi-Level Task Ladder.'' \textit{CoRL 2026} (Under Review).
    \begin{cvitems}
    \item Engineered a \textbf{GPU-accelerated simulation environment} for ManiLadder, featuring 112 tasks with four difficulty tiers.
    \item Implemented standardized metrics and MILE for rigorous evaluation of manipulation intelligence across diverse robotic embodiments.
    \end{cvitems}
  \item Haziq Razali, \textbf{Yuxuan Zhang}, Qianli Xu, Yiannis Demiris. ``Learning to Synthesize Novel Human-Object Interaction in Collaborative Task-Based Settings.'' \textit{AAAI 2026 Workshop HCM Submission}.
    \begin{cvitems}
    \item Developed a multi-view perception pipeline using 4D-Humans, HaMeR, and SAM-6D to reconstruct high-fidelity 3D human-object trajectories.
    \item Investigated \textbf{LLM-guided task decomposition} to facilitate multi-agent motion forecasting and synthesis for long-horizon collaborative tasks.
    \end{cvitems}
\end{enumerate}

% ===== Experience =====
\section{Selected Experience}

\cventry{Research Intern (Hardware / Software / System Design)}{AMD Singapore}{Singapore}{Mar 2026 -- Aug 2026}
\begin{cvitems}
  \item Incoming research internship focusing on high-performance system architecture for AI workloads (subject to NDA).
\end{cvitems}

\cventry{AI Research Intern}{Fatfish AI}{Singapore}{Oct 2025 -- Dec 2025}
\begin{cvitems}
\item Developed a ROS2-based end-to-end deployment pipeline for humanoids, integrating MiniPC, RealSense, and Jetson Orin Nano.
\item Implemented and analyzed \textbf{Sim2Real transfer} of VLA policies for locomotion and manipulation, utilizing RL-based controllers and IK solvers.
\end{cvitems}

\cventry{Research Intern (Assistive Robotics)}{AdaComp Lab, National University of Singapore}{Singapore}{Jun 2025 -- Sep 2025}
\begin{cvitems}
\item Engineered a quadrupedal assistant system (RDog-V2) featuring 360$^\circ$ LiDAR and panoramic vision for blind-aid navigation.
\item Optimized LiDAR-based \textbf{SLAM and dynamic obstacle avoidance} algorithms to enable safe, autonomous guidance in complex urban settings.
\end{cvitems}

\cventry{Research Intern (Human-Behaviour Understanding)}{I2R, A*STAR}{Singapore}{Mar 2025 -- Dec 2025}
\begin{cvitems}
\item Formulated a data-generation framework for Human-Object Interaction (HOI) by synthesizing multi-view RGB-D data with LLM-based reasoning.
\item Refined 3D reconstruction techniques to model complex collaborative behaviors, supporting research into human-centric robot learning.
\end{cvitems}

\cventry{R\&D Intern (Computer Vision)}{Changjiang Intelligent Control Co., Ltd.}{China}{Jul 2021 -- Aug 2021}
\begin{cvitems}
\item Designed a stereo-vision system for real-time 3D surface reconstruction and \textbf{6-DoF pose estimation} in automated industrial maintenance.
\end{cvitems}

\cventry{Tech Art Intern}{Boke City Co., Ltd. (Wuhan Branch)}{China}{Jan 2021 -- Feb 2021}
\begin{cvitems}
\item Investigated physics-based character-environment interactions in Unity, focusing on the synthesis of realistic combat visual effects via C\# scripts.
\end{cvitems}

\section{Selected Projects}

\cventry{Automated Calibration System for A/D Modules}{Undergraduate Thesis, Harbin Institute of Technology}{China}{Oct 2023 -- May 2024}
\begin{cvitems}
\item Developed a multi-channel selection system (PCB + Firmware) and automated PXIe-based calibration protocols for high-precision A/D modules.
\end{cvitems}

\cventry{Autonomous Drone Docking \& Charging Platform}{Innovation Training Program, HIT}{China}{Oct 2021 -- Sep 2022}
\begin{cvitems}
\item Engineered a precision landing system (DJI M100 + OpenMV) utilizing \textbf{GPS-denied localization} via AprilTag and PID-based control.
\end{cvitems}

\cventry{Interactive 3D Port Reconstruction}{Annual Research Project, HIT}{China}{Oct 2020 -- Sep 2021}
\begin{cvitems}
\item Synthesized large-scale port environments in Unity using high-resolution heightmaps and satellite data.
\item Implemented immersive VR interfaces and weather simulation systems to study human-computer interaction in digital twins.
\end{cvitems}

% \section{References}
% {\small
%   \renewcommand{\arraystretch}{1.12}
%   \begin{tabularx}{\linewidth}{@{}p{0.15\linewidth}XXX@{}}
%     \textbf{Name} & Lin SHAO & Muhammad Haziq BIN RAZALI & Shengwei MENG \\
%     \textbf{Affiliation} & National University of Singapore & Agency for Science, Technology and Research & Harbin Institute of Technology \\
%     \textbf{Email Address} & \href{mailto:linshao@nus.edu.sg}{linshao@nus.edu.sg} & \href{mailto:haziqmr@a-star.edu.sg}{haziqmr@a-star.edu.sg} & \href{mailto:mengsw@hit.edu.cn}{mengsw@hit.edu.cn} \\
%     \textbf{Phone Number} & (65) 6516-2908 & (65) 9172-2319 & (86) 133-9156-7225 \\
%     \textbf{Relationship} & Master’s research supervisor & Research internship mentor & Undergraduate thesis supervisor
%   \end{tabularx}
% }

\end{document}